%to do
\section{background}
\label{sec:background}
\subsection{cloud computing}

\subsection{burst buffer}
In modern high performance systems storage systems can easily become the bottleneck of the whole system\xtq{citation}, 
\subsection{workflow application}
Montage is a toolkit developed by Spitzer Science Center for assembling Flexible Image Transport System (FITS) images into custom mosaics.
It has been built, tested and the output products validated by Montage customers on Unix platforms, including Linux, Solaris, Mac OSX, and IBM AIX.
It has been used to generate mosaics from data released by the Spitzer Space Telescope, the Hubble Space Telescope, the Infrared Astronomical Satellite (IRAS),
the Midcourse Space Experiment (MSX), the Sloan Digital Sky Survey (SDSS), and ground-based telescopes such as the National Optical Astronomy Observatories (NOAO) 4-m telescope and the William Herschel 4-m telescope.

The Persistence of Vision Raytracer, or POV-Ray, is a ray tracing program which generates images from a text-based scene description,
and is available for a variety of computer platforms. It was originally based on DKBTrace, written by David Kirk Buck and Aaron A.
Collins for the Amiga computers.
There are also influences from the earlier Polyray raytracer contributed by its author Alexander Enzmann.
POV-Ray is free and open-source software with the source code available under the AGPLv3.
Many methods for generating the 3-D models are used, including a companion program "moray" for interactive modeling.

